Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-05-15 manuscript/manuscript.tex
Edited Example with real data in manuscript

@@

Besides all the tests we have carried out on the new code, we intend to show a forward modelling example with real data.
In order to do that we have chosen the Neuqu\'en Basin: a sedimentary basin located to the east of the Andes, between 32$^\circ$S and 40$^\circ$S latitude (see Figure \ref{fig:neuquen-basin}a), that includes continental and marine siliciclastics, carbonates and evaporites accumulated over the Jurassic and the Cretaceous constituting a stratigraphic record up to 5000m of depth \citep{Howell2005}.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin.pdf}
\caption{
         Forward model example with real data: Nequ\'en sedimentary modelled through tesseroids with exponential density.
         (a) Topography of Neuqu\'en Basin (in km),
         (b) Thickness of the sedimentary basin (in meters),
         (c)-(h) Computed gravity fields: potential $V$ (in J/kg), gradient components $g_x$, $g_y$ and $g_z$ (in mGal) and Marussi tensor components $g_{xy}$ and $g_{zz}$ (in Eötvös), calculated at 50km of height over the ellipsoid.}
\label{fig:neuquen-basin}
\end{figure*}

The thickness of the sediment pack was obtained from \citet{Heine2007}.
We managed to produce a regular grid with a resolution of 0.05$^\circ$ on both longitude and latitude directions with one value of thickness on each node (see Figure \ref{fig:neuquen-basin}b).

@@

We must also define a density function for the entire model.
\citet{Sigismondi2012} proposed a minimum and maximum density contrast for the Neuqu\'en basin of -412kg/m$^3$ and -275kg/m$^3$, respectively. \todo[inline]{ver que esos valores son de contraste y tienen q ir negativos. poner los valores absolutos.}
So we have chosen, for this specific example, an exponential density (like the one in equation \ref{eq:density-exp}) that assumes the minimum value on the surface and the maximum at 5858m, i.e. the bottom of the basin, with a value of $b$ equal to 3km.

We have finally computed the gravity potential $V$, the gradient components $g_x$, $g_y$ and $g_z$, and the Marussi tensor components $g_{xy}$ and $g_{zz}$ on a computation grid of 159$\times$163 nodes with a 0.05$^\circ$ spacing on both longitude and latitude directions at a 50km height over the reference ellipsoid.
The resulting gravity fields can be seen in Figures \ref{fig:neuquen-basin}c-h.
We have excluded the other components of the Marussi tensor from the Figure, although they can be found in the repository.

>>>>

\todo[inline]{I'm thinking to remove the speed comparison}

@@

Besides all the tests we have carried out on the new code, we intend to show a 
forward modelling example with real data.

Besides the determination of the distance-size and the delta ratio, we 
wanted to show how the algorithm performs under a real data forward model.
In order to do it we have chosen the Neuqu\'en Basin: a sedimentary basin 
located to the east of the Andes, between 32$^\circ$S and 40$^\circ$S latitude 
(see Figure \ref{fig:neuquen-basin}a), that includes continental and marine 
siliciclastics, carbonates and evaporites accumulated over the Jurassic and 
the Cretaceous constituting a stratigraphic record up to 5000m of depth 
\citep{Howell2005}.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin.pdf}
\caption{
    Forward model example with real data: Nequ\'en sedimentary modelled 
    through tesseroids with exponential density.
    (a) Topography of Neuqu\'en Basin (in km),
    (b) thickness of the sedimentary basin (in meters),
    (c) density function used to model the basin (depth in km and density in 
    kg/m$^3$),
    (d)-(l) computed gravity fields: potential $V$ (in J/kg), gradient 
    components $g_x$, $g_y$ and $g_z$ (in mGal) and Marussi tensor components 
    (in Eötvös), calculated at 50km of height over the ellipsoid.}
\label{fig:neuquen-basin}
\end{figure*}

The thickness of the sediment pack was obtained from \citet{Heine2007}.
We managed to produce a regular grid with a resolution of 0.05$^\circ$ on both 
longitude and latitude directions with one value of thickness on each node 
(see Figure \ref{fig:neuquen-basin}(b).

@@

We must also define a density function for the entire model.
\citet{Sigismondi2012} proposed a minimum and maximum density contrast for the 
Neuqu\'en basin of -412kg/m$^3$ and -275kg/m$^3$, respectively. 
So we have chosen, for this specific example, an exponential density (like the 
one in equation \ref{eq:density-exp}) that assumes the minimum value on the 
surface and the maximum at 5858m, i.e. the bottom of the basin, with a value 
of $b$ equal to 2km.
This density function can be seen on Figure \ref{fig:neuquen-basin}(c).

We have computed the gravity potential $V$, the gradient components $g_x$, 
$g_y$ and $g_z$, and the Marussi tensor components $g_{xx}$, $g_{xy}$, 
$g_{xz}$, $g_{yy}$  and $g_{zz}$ on a computation grid of 159$\times$163 nodes 
with a 0.05$^\circ$ spacing on both longitude and latitude directions at a 
50km height over the reference ellipsoid.
The resulting gravity fields can be seen in Figures 
\ref{fig:neuquen-basin}(d)-(l).
We have excluded the other components of the Marussi tensor from the Figure, 
although they can be found in the repository.
